Formal Analysis of EDHOC Key Establishment for Constrained IoT Devices

### 2022-07-18 paper.tex
Changes to section 3

Note: Section 5.2.2 says:
"The Initiator MUST NOT change the supported cipher suites and
the order of preference in SUITES_I based on previous error messages."
But: what happens if order of preference changes for some other reason? Would it
be good it include a flag in msg1 to indicate to the responder that the
ciphersuite order depends on a previous run? This way, responder could react
differently if a new cipher suite has been added without breaking the "MUST NOT"
requirement. Need to think about this more.

>>>>

Note: Section 5.2.2 says:
"The Initiator MUST NOT change the supported cipher suites and
the order of preference in SUITES\_I based on previous error messages."
But: what happens if order of preference changes for some other reason? Would it
be good it include a flag in msg1 to indicate to the responder that the
ciphersuite order depends on a previous run? This way, responder could react
differently if a new cipher suite has been added without breaking the "MUST NOT"
requirement. Need to think about this more.
